Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-07 paper.tex
Spellcheck run.

{\bf \cite{berenson2011task} presents a formal proof that projection-based 
constrained random motion planning on a fixed dimension manifold is 
probabilisticaly complete. This proof applies to our algorithm. }

>>>>

{\bf \cite{berenson2011task} presents a formal proof that projection-based 
constrained random motion planning on a fixed dimension manifold is 
probabilistically complete. This proof applies to our algorithm. }
